---
title: "Treasure Hunt Analysis"
author: "DVM Bishop & Adam Parker"
date: "10/02/2020"
output:
  pdf_document: default
  html_document: default
---

# Location game accuracy

This R markdown details the analysis for Response Times analysis detailed in the preregistration for the project "Impact of Training Schedules on Language Learning in Children". This study was preregistered on the Open Science Framework (https://osf.io/ykacn/). 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
# libraries 
library("effects")
library("dplyr")
library("lme4")
library("yarrr")
library("ggplot2")
library("pscl")
library("MASS")
library("COMPoissonReg")
library("VGAM")
library("glmmTMB")
library("mgcv")
library("readr")
library("knitr")
library("ggpubr")#for density plots
```

## Output file from Gorilla

This is csv file with a row for each datapoint in the series of trials. Subjects, identified by random letter strings, are stacked on top of each other.  We start by reading the data and cutting out unwanted information. This file was combined using the "combined_files_v13.R" script and cases meeting our data exclusion criteria were removed.

```{r readdata}
child_RT_full <- read_csv("Treasure_Hunt_Data_Final.csv")

#rename variables
wc<-which(names(child_RT_full) %in% c("Event Index","Time Elapsed","Time Taken","Clue1"))
names(child_RT_full)[wc]<-c("event","time.elapsed","RT","item")


# relabel variables and set some to factors
child_RT_full$subject <- as.factor(child_RT_full$subject)
child_RT_full$item <- as.factor(child_RT_full$item)
child_RT_full$condition <- as.factor(child_RT_full$condition)
child_RT_full$Attempts <- as.numeric(child_RT_full$Attempts)
child_RT_full$Mistakes <- as.numeric(child_RT_full$Mistakes)

child_RT_full$RT <- as.numeric(child_RT_full$RT)
child_RT_full$event <- as.numeric(child_RT_full$event)
child_RT_full$Vocab <- as.factor(child_RT_full$Vocab)
levels(child_RT_full$Vocab) <- c("preposition", "vocabulary")

child_RT_full$subcode<-paste0(child_RT_full$condition,"_",levels(child_RT_full$subject))

age <- aggregate(FUN= mean, data= child_RT_full, year_age~ subject)
sd(age$year_age)
```

```{r reformatdf}
# Make a column that has same number for all rows that belong to one trial
# In a loop - a bit slow, but easy to understand and program

# Redo code for PLACE so we can identify first place response - we'll use this only for correct trials, but it gives an RT for the start of any response, which is less confounded by number/distance to place things
# In same loop, make columns for N slots open, and N elements to move (for vocab these are always 1 and 1, but for prepositions, this varies)

# NB because 'between' has different correct options, it will get N elements count of 4

# Would be good to have Gorilla record the spreadsheet, as we could then easily categorise items.
# We could identify the prepositions from string manipulation of 'item' if necessary....

i=1
child_RT_full$trial<-NA #initialise trial col
child_RT_full$slots <- NA
child_RT_full$elements <- NA

#find columns with grid slots 
gridcols<-which(colnames(child_RT_full)%in% c('A1','A2','A3','A4','B1','B2','B3','B4',
'C1','C2','C3','C4','D1','D2','D3','D4'))
elementcols <- which(colnames(child_RT_full) %in% c('Answer1Cell','Answer2Cell','Answer3Cell','Answer4Cell'))

child_RT_full$trial[1]<-1
nrow<-nrow(child_RT_full)

i=0
for (n in 1:nrow){
  if (n>1){
  if(child_RT_full$subject[n] != child_RT_full$subject[(n-1)])
  {i = 0}
  }
  if(child_RT_full$Type[n]=='START PUZZLE') #counter simply increments on each 'START PUZZLE' row
  {i <- i +1
  child_RT_full$Type[n+1] <- 'PLACE1'} #next event after START PUZZLE is distinguished
  child_RT_full$trial[n] <- i
  
  child_RT_full$slots[n] <- length(which(child_RT_full[n,gridcols]=='open'))
  child_RT_full$elements[n]<-4-length(which(is.na(child_RT_full[n,elementcols])))
}

# Now we'll aim to create a new file with just the information we need, in a sensible order
# Start by selecting column of interest - we'll do this in a loop so we can control the order of columns 
wanted<-c("X1"  ,"subject" , "month_age","event"  ,"trial","Vocab","condition", "Type", "item","slots","elements","time.elapsed", "RT",  "Attempts","Correct","Mistakes")
mycol <- vector() #initialise blank vector
for (i in 1:length(wanted)){
  mycol<-c(mycol,which(names(child_RT_full) == wanted[i])) #find colnumbers of wanted
}
child_RT_wanted <- child_RT_full[,mycol]


#  glimpse(child_RT_wanted) #uncomment to see list of contents of cols
allsub<-unique(child_RT_wanted$subject)
nsub <- length(allsub) #count the number of subjects
print(paste("Number of subjects = ",nsub) ) 
```


```{r prunetrials}

child_RT_short <- filter(child_RT_wanted,Type %in% c('PLACE1','PUZZLE COMPLETE'))
child_RT_short$RTpick <- NA #initialise column to hold RT for picking first item
# We'll now move the time.elapsed alongside PUZZLE COMPLETE
w<-which(child_RT_short$Type=='PUZZLE COMPLETE')
child_RT_short$RTpick[w]<-child_RT_short$time.elapsed[(w-1)]

# Now can get rid of rows with PLACE1
child_RT_short <- filter(child_RT_short,Type == c('PUZZLE COMPLETE'))
# Create new column for correct RT.
# Puzzling that time elapsed and RT are not the same for PLACE1, but are for PUZZLE COMPLETE
# We think this is an error, but it does not affect us as we have not used that RT.

#Now split into vocab and preposition files, as these are so different that it is best to treat them separately

vocabdat <- filter(child_RT_short,Vocab=='vocabulary')
prepdat <- filter(child_RT_short,Vocab=='preposition')

#Quick check of RTs: correct only - confirms that RTpick equals RT
 vocabcorr<-filter(vocabdat,Correct==1)
#plot(vocabcorr$RT[1:2000],vocabcorr$RTpick[1:2000]) #uncomment to see this
#abline(a=0,b=1)
```

Preposition types are identified by hard coding here: beware if using with different spreadsheets. Here we just export a list of all items, and manually assign to item type.
NB This is not used in Nicole analysis, but analysing this way made it clear there would be problems in using the preposition task to look at learning. 

```{r findpreptype}
write.csv(levels(prepdat$item),'preptypes.csv')
#####!!!!!  HARD CODED !!!! BEWARE
preptype<-c(0,0,0,0,0,0,0,0,0,0,3, 4, 1, 2, 2, 3, 2, 3, 1, 2, 3, 1, 3, 3, 1, 4, 3, 3, 4, 1, 2, 3, 1, 3, 1, 3, 1, 2, 3, 2, 2, 2, 3, 1, 4, 4, 3, 3, 3, 1, 4, 3, 3, 1, 4, 2, 3, 4, 1, 3)
#The first 10 are vocab items
#1 = above
#2 = below
#3 = between
#4 = next to +
prepdat$senttype <- 0
for (i in 1:nrow(prepdat)){
  m <- which(levels(prepdat$item)==prepdat$item[i])
  prepdat$senttype[i] <- preptype[m]
}

```
For vocabulary, the main measure of learning is accuracy, so we'll first plot that to see how it changes with training, and whether it differs by conditions.
In fact, 'attempts' could be used to give a more graded measure of accuracy.
Let's break into blocks of 10 trials and measure total attempts within a block.

```{r makeblock}
# Because of interleaving, trial number can't be used to recode to block, but can just paste in code that identifies 10 trials in a row.
# NB this is referred to a 'block' here, but for the interleaved items, they will be alternate trials. Since we have pulled vocabulary data into a separate file, the method will work for these data as well as for those from blocked condition.
nrow <- nrow(vocabdat)
vocabdat$block <-0 #initialise
blocksize <- 10
blockassign<- rep(seq(1:30),1,each=blocksize) # makes 111112222233333 etc 30 times

for (s in 1:nsub){
  thissub <- allsub[s]
  w <- which(vocabdat$subject==thissub) #find row range for each subject
  firstrow<-w[1]
  lastrow<-max(w)
  sublen <-lastrow-firstrow+1
  vocabdat$block[w]<-blockassign[1:sublen] #paste in as many rows from blockassign as needed
}

# 
myblockvoc <- as.data.frame.matrix(table(vocabdat$subject,vocabdat$block)) #shows how many blocks done by each.
colnames(myblockvoc)<-c('N.b1','N.b2','N.b3','N.b4','N.b5','N.b6','N.b7')
myblockvoc$b1 <-0
myblockvoc$b1[myblockvoc$N.b1==10]<-1
myblockvoc$b2 <-0
myblockvoc$b2[myblockvoc$N.b2==10]<-1
myblockvoc$b3 <-0
myblockvoc$b3[myblockvoc$N.b3==10]<-1
myblockvoc$b4 <-0
myblockvoc$b4[myblockvoc$N.b4==10]<-1
myblockvoc$b5 <-0
myblockvoc$b5[myblockvoc$N.b5==10]<-1
#Most have done 4  ; can vary the N analysed for plots below by changing selection.

Ncomplete <- colSums(myblockvoc[,8:12])
print('N completing given number of Vocabulary blocks:') 
print(Ncomplete)

#find those who did 4 or more blocks
includesubs<-which(myblockvoc$b4==1)
subinclude <- row.names(myblockvoc)[includesubs]




# Repeat block analysis for prepositions (not needed for analysis now)
nrow <- nrow(prepdat)
prepdat$block <-0 #initialise
blocksize <- 10
blockassign<- rep(seq(1:30),1,each=blocksize) # makes 111111111122222222223333333333 etc 30 times

for (s in 1:nsub){
  thissub <- allsub[s]
  w <- which(prepdat$subject==thissub) #find row range for each subject
  firstrow<-w[1]
  lastrow<-max(w)
  sublen <-lastrow-firstrow+1
  prepdat$block[w]<-blockassign[1:sublen] #paste in as many rows from blockassign as needed
}

# 
#table(prepdat$subject,prepdat$block) #shows how many blocks done by each.


```

## Process RTs

We anticipate non-normal RT data.
We will inspect the data and compare impact of various ways of handling this.
To do this we will first just focus on the correct responses to Vocabulary items.
We will look at these separately for each subject.

Two functions created to a) remove outliers, and b) plot data

```{r Hoaglin_iglewicz}
#Outliers are defined in terms of quartiles: those that are more than 2.2 times away #from range which is difference between 25th and 75th centile
#Hoaglin, D. C., & Iglewicz, B. (1987). Fine tuning some resistant rules for outlier labeling. Journal of American Statistical Association, 82(400), 1147–1149

HIoutliers<-function(myvector,cutoff){
#standard cutoff is 2.2, but can be lower if all outliers are in one diretion
lower_quartile <- quantile(myvector, probs=0.25, na.rm="TRUE")
upper_quartile <- quantile(myvector, probs=0.75, na.rm="TRUE")
quartile_diff <- upper_quartile - lower_quartile

lower_limit <- lower_quartile - cutoff*quartile_diff
upper_limit <- upper_quartile + cutoff*quartile_diff
myvector_marked<-myvector
myout<-data.frame(myvector,myvector_marked)
w<-c(which(myvector_marked<lower_limit),which(myvector_marked>upper_limit))

myout$myvector_marked[w]<-NA #returns a dataframe which has original data in first column, and same data with outliers removed in 2nd column

return(myout)
}
```

# Function to check normality for each subject/vocab
```{r normplot}
#This now modified to be separate for vocab 
mydensityplot <- function(mydf,sub1,sub2,RTcol,showplot){ #specify df,range of subs and column number to inspect
okcount<-0 #initialise counter for ns p-values, i.e. normal 
mycounter<-0 #initialise counter for N times through loop

  par(mfrow=c(2,2)) #output in 2 rows, 2 cols
  for (i in sub1:sub2){
    subname<-allsub[i]
    mycounter<-mycounter+1
     myrows<-which(mydf$subject==subname) #select rows for this sub
     temp<-data.frame(mydf[myrows,])
    myRT<-temp[,RTcol]

    d=density(myRT,na.rm=TRUE)
    if(showplot==1){
      title<- paste0(subname,': ', levels(temp$Vocab)[j],' \nNormality test p-value: ',round(shapiro.test(myRT)$p.value,3))
    plot(d,main = title,xlab=names(temp)[RTcol])
    }
    if(shapiro.test(myRT)$p.value>.05){
      okcount<-okcount+1
    }
  }

mymessage<-paste0(okcount,' out of ',mycounter,' meet p>.05 criterion for normality')
return(mymessage)
}


```

We use these two functions to consider how transforming data and removing outliers affects normality of RT distribution.
This involves creating additional columns with different versions of RT.

```{r compareRT}

#Start with regular RT for correct only
mydf <- vocabdat
sub1 <- 1
sub2 <- 96
RTcol <- which(names(mydf)=='RTpick')
mydf <- filter(mydf,Mistakes==0)
showplot <-0
 mymessage<-mydensityplot(mydf,sub1,sub2,RTcol,showplot)
 print(paste0('Raw RT pick: ',mymessage))
       
 #Truncation
 RTlimit<-20000
 RTlowlimit<-200
 #Before outlier removal by formula, just reset any > limit (e.g. 20000 (20 sec)) to that limit
 vocabdat$RTpick.a <- vocabdat$RTpick #initialise column
 w<-c(which(vocabdat$RTpick.a > RTlimit),which(vocabdat$RTpick.a<RTlowlimit))
 vocabdat$RTpick.a[w] <- RTlimit
 #recheck normality
 RTcol <- which(names(vocabdat)=='RTpick.a')
 mydf <- filter(vocabdat,Mistakes==0)
 showplot <-0
 mymessage <- mydensityplot(mydf,sub1,sub2,RTcol,showplot)
 print(paste0('Censored RTpick (RTpick.a): ',mymessage))
  
 #Remove outliers with Hoaglin-Iglewicz
 HIlimit <- 1.65 #this num is the distance from interquartile range used for exclusion
 # -2.2 is recommended level, but that is with outliers at both ends

 RTcol<-which(names(vocabdat)=='RTpick.a') #number of column with RTcorr.a data
 myvector <-unlist(vocabdat[,RTcol]) #unlist needed as must be vector, not data frame
 RTkeep<-HIoutliers(myvector,HIlimit)  #run HIoutliers function
 vocabdat$RTpick.k<-RTkeep[,2] #add a column which has NA for RT outliers

RTcol<-which(names(vocabdat)=='RTpick.k')
mydf <- filter(vocabdat,Mistakes==0)
mymessage <- mydensityplot(mydf,sub1,sub2,RTcol,showplot)
print(paste0('Outlier exclusion Hoaglin Iglewicz 1.65 (RTpick.k): ',mymessage))
 
 #THis still has several with a long tail
 #Try with log transform - apply first to all RTs (as may use these later)
 vocabdat$logRTpick.k<-log(vocabdat$RTpick.k)

RTcol<-which(names(vocabdat)=='logRTpick.k')
mydf <- filter(vocabdat,Mistakes==0)
mymessage <- mydensityplot(mydf,sub1,sub2,RTcol,showplot)
print(paste0('Logs after censoring/HI outliers (logRTpick.k): ',mymessage))

#We preregistered analysis using RTpick.k, so will use that (even though the log version is more normal)

# get RTpick.k for prep
showplot <-0
 mymessage<-mydensityplot(mydf,sub1,sub2,RTcol,showplot)
 print(paste0('Raw RT pick: ',mymessage))
       
 #Truncation
 RTlimit<-20000
 RTlowlimit<-200
 #Before outlier removal by formula, just reset any > limit (e.g. 20000 (20 sec)) to that limit
 prepdat$RTpick.a <- prepdat$RTpick #initialise column
 w<-c(which(prepdat$RTpick.a > RTlimit),which(prepdat$RTpick.a<RTlowlimit))
 prepdat$RTpick.a[w] <- RTlimit
 #recheck normality
 RTcol <- which(names(prepdat)=='RTpick.a')
 mydf <- filter(prepdat,Mistakes==0)
 showplot <-0
 mymessage <- mydensityplot(mydf,sub1,sub2,RTcol,showplot)
 print(paste0('Censored RTpick (RTpick.a): ',mymessage))
  
 #Remove outliers with Hoaglin-Iglewicz
 HIlimit <- 1.65 #this num is the distance from interquartile range used for exclusion
 # -2.2 is recommended level, but that is with outliers at both ends

 RTcol<-which(names(prepdat)=='RTpick.a') #number of column with RTcorr.a data
 myvector <-unlist(prepdat[,RTcol]) #unlist needed as must be vector, not data frame
 RTkeep<-HIoutliers(myvector,HIlimit)  #run HIoutliers function
 prepdat$RTpick.k<-RTkeep[,2] #add a column which has NA for RT outliers

RTcol<-which(names(prepdat)=='RTpick.k')
mydf <- filter(prepdat,Mistakes==0)
mymessage <- mydensityplot(mydf,sub1,sub2,RTcol,showplot)
print(paste0('Outlier exclusion Hoaglin Iglewicz 1.65 (RTpick.k): ',mymessage))
 
 #THis still has several with a long tail
 #Try with log transform - apply first to all RTs (as may use these later)
 prepdat$logRTpick.k<-log(prepdat$RTpick.k)

RTcol<-which(names(prepdat)=='logRTpick.k')
mydf <- filter(prepdat,Mistakes==0)
mymessage <- mydensityplot(mydf,sub1,sub2,RTcol,showplot)
print(paste0('Logs after censoring/HI outliers (logRTpick.k): ',mymessage))
```

```{r excludesubs}
#make vocshort which has only included cases, and only up to block4
vocshort<-vocabdat[vocabdat$subject%in%subinclude,]
vocshort<-vocshort[vocshort$block<5,] 
prepshort<-prepdat[prepdat$subject%in%subinclude,]
prepshort<-prepshort[prepshort$block<5,]

# recode attempts for prepositions
prepshort <- prepshort %>% mutate(Attempts = ifelse(block == 1, Attempts, Attempts-1))

short <- bind_rows(prepshort, vocshort)
# code correct as 1 or 0
short[c("Correct")][is.na(short[c("Correct")])] <- 0
```

Now plot means

```{r plots}
# now create aggregate data
agg_dat <- 
  short %>%
   group_by(condition, block, Vocab) %>%
    summarise(meanRT = mean(RTpick.k, na.rm = TRUE),
              sdRT = sd(RTpick.k, na.rm = TRUE),
              meanAcc = mean(Correct, na.rm = TRUE),
              sdAcc = sd(Correct, na.rm = TRUE),
              meanAtt = mean(Attempts, na.rm= TRUE),
              sdAtt = sd(Attempts, na.rm= TRUE),
              count = n()) %>%
    mutate(seRT = sdRT / sqrt(count),
           seAcc = sdAcc / sqrt(count),
           seAtt = sdAtt / sqrt(count),
           lower_ci_RT = meanRT - qt(1 - (0.05 / 2), count - 1) * seRT,
           upper_ci_RT = meanRT + qt(1 - (0.05 / 2), count - 1) * seRT,
           lower_ci_Acc = meanAcc - qt(1 - (0.05 / 2), count - 1) * seAcc,
           upper_ci_Acc = meanAcc + qt(1 - (0.05 / 2), count - 1) * seAcc,
           lower_ci_Att = meanAtt - qt(1 - (0.05 / 2), count - 1) * seAtt,
           upper_ci_Att = meanAtt + qt(1 - (0.05 / 2), count - 1) * seAtt)

levels(agg_dat$Vocab) <- c("Comprehension", "Vocabulary")

RT_plot <- ggplot(agg_dat, aes(x=block, y=meanRT, group=condition, color=condition)) + 
  geom_errorbar(aes(ymin=lower_ci_RT, ymax=upper_ci_RT), width=.1, position = position_dodge(width=0.25)) +
  geom_line(position = position_dodge(width=0.25)) +
  geom_point(position = position_dodge(width=0.25)) +
  theme_bw(18) +
  scale_y_log10() + 
  ylab("Reaction time (ms)") + 
  xlab("Block of 10 items") +
  ggtitle("(B)") +
  theme(legend.position="top", legend.title = element_blank(), plot.title = element_text(hjust = 0.5)) + 
  facet_wrap(~Vocab)
Attempt_plot <- ggplot(agg_dat, aes(x=block, y=meanAtt, group=condition, color=condition)) + 
  geom_errorbar(aes(ymin=lower_ci_Att, ymax=upper_ci_Att), width=.1, position = position_dodge(width=0.25)) +
  geom_line(position = position_dodge(width=0.25)) +
  geom_point(position = position_dodge(width=0.25)) +
  theme_bw(18) +
  ylab("Number of attempts") + 
  xlab("Block of 10 items") +
  ggtitle("(A)") +
  theme(legend.position="top", legend.title = element_blank(), plot.title = element_text(hjust = 0.5))+ 
  facet_wrap(~Vocab)
Accuracy_plot <- ggplot(agg_dat, aes(x=block, y=meanAcc, group=condition, color=condition)) + 
  geom_errorbar(aes(ymin=lower_ci_Acc, ymax=upper_ci_Acc), width=.1, position = position_dodge(width=0.25)) +
  geom_line(position = position_dodge(width=0.25)) +
  geom_point(position = position_dodge(width=0.25)) +
  theme_bw(18) +
  ylab("Number of attempts") + 
  xlab("Block of 10 items") +
  ggtitle("(A)") +
  theme(legend.position="top", legend.title = element_blank(), plot.title = element_text(hjust = 0.5))+ 
  facet_wrap(~Vocab)
# combine
ggpubr::ggarrange(Attempt_plot, RT_plot)
```

# HYPOTHESIS 1: Learning

Reaction Time Analysis:

In order to investigate Hypothesis 1, we will use beta estimates (regression slopes) to estimate learning for spatial preposition and vocabulary items. This will be achieved by fitting a linear model to median RTs for blocks of 10 successive trials. For preposition and vocabulary items separately, we will then conduct a one-tailed one-sampled t-test where participant slopes are compared to 0 (indicating that no learning has occurred). Because reaction time decreases as learning occurs, learning is said to have occurred if the sample gradients are significantly less than 0.

In the Reaction Time analysis, we plan to only consider the trials in which the participants successfully completed the trial on their first attempt unless this results in a substantial loss of data

```{r analyseslopes}
#Slopes for correct responses based on median RTpick.k by block
corrvocab <- filter(vocshort,Mistakes==0)
vocmedians<-aggregate(RTpick.k~ block+subject+condition, data= corrvocab, FUN= median)
colnames(vocmedians)<-c('block','subject','condition','RTpick.k')

#create column for age band, also age in months for later Ancova
vocmedians$ageband <- 1
vocmedians$age <- NA
for (i in 1:nrow(vocmedians)){
  w<-vocmedians$subject[i]
  w1<-which(vocshort$subject ==w)
  thisage<-vocshort$month_age[w1[1]]
  if(thisage>95)
    {vocmedians$ageband[i] <- 2}
  vocmedians$age[i] <- thisage
}

vocmedians$slope <- NA #dummy column
vocmedians$gain <- NA

 blocklist <- seq(1:4)
 nsubkeep<-length(subinclude)
for (i in 1:nsubkeep){ #loop through subjects
  subname<-subinclude[i] #find subject ID
   myrows<-which(vocmedians$subject==subname) #select rows for this sub
   temp<-vocmedians$RTpick.k[myrows] #make a little vector with this subject's data
   theseblocks<-vocmedians$block[myrows]
   mylm <- summary(lm(log10(temp)~theseblocks))
   vocmedians$slope[myrows[1]]<- mylm$coefficients[2,1]
}
print("one-group t-test vs zero for slopes")
t.test(vocmedians$slope[vocmedians$condition=='blocked'])
lsr::cohensD(vocmedians$slope[vocmedians$condition=='blocked'], mu= 0)
t.test(vocmedians$slope[vocmedians$condition=='interleaved'])
lsr::cohensD(vocmedians$slope[vocmedians$condition=='interleaved'], mu= 0)

print("T test comparing slopes")
t.test(vocmedians$slope ~ vocmedians$condition)
# bayes
slope_no_na <- vocmedians %>% tidyr::drop_na(slope)
lsr::cohensD(vocmedians$slope ~ vocmedians$condition)
bf = BayesFactor::ttestBF(formula= slope ~ condition, data= slope_no_na)
bf

summary(lm(data= vocmedians, slope~ condition * age))

change_RT <- ggplot(vocmedians, aes(x=condition, y=slope, fill=condition, shape= condition, linetype= condition)) +
  geom_violin(alpha= .1, size=1) +
  geom_hline(yintercept=0, linetype="dashed",  color = "black", size=1) + 
  geom_dotplot(binaxis='y', stackdir='center', dotsize=1,alpha= 0.8) + 
  geom_boxplot(width=0.1, position=position_dodge(0.9), size=1 , notch = T, notchwidth = 0.4, varwidth =F,
               fill= 'white', color= 'black', show.legend=FALSE, linetype= 'solid') +
  theme_bw(18) + xlab(" ") + ylab("Beta-estimates: Reaction times") + theme(legend.position="top") +
  theme(legend.position = 'none', legend.title=element_blank(), plot.title = element_text(hjust = 0.5)) + ggtitle("(B)") + 
  ylim(-.13, .13)
```

Accuracy Analysis:

To address hypothesis 1, for each of the 4 conditions, the number of attempts to successfully complete the tasks will be averaged across the first 10 trials, and across the last 10 trials separately. The two averages will then be compared using a paired-sample t-test. Learning is said to have occurred if the average number of attempts of the last 10 trials is significantly lower than that for the first 10 trials. That said, we do note that there is a possible floor effect in the analysis of this dependent variable which may mask learning.

```{r accuracygain}
#aggregate attempts by block
vocerrs<-aggregate(Attempts~ block+subject+condition, data= vocshort, FUN= mean)
colnames(vocerrs)<-c('block','subject','condition','attempts')

## THIS IS FROM NICOLE'S THESIS ##
vocerrs$decline <-NA
for (i in seq(1,nrow(vocerrs),by=4)){
  vocerrs$decline[i]<-vocerrs$attempts[i+3]-vocerrs$attempts[i]
}

print("one-group t-test vs zero for attmept reduction")
t.test(vocerrs$decline[vocerrs$condition=='blocked'], alternative= "less")
t.test(vocerrs$decline[vocerrs$condition=='interleaved'], alternative= "less")

print("T test comparing interleaved and blocked error decline block 1 to 4")
t.test(vocerrs$decline ~ vocerrs$condition)
bf2 = BayesFactor::ttestBF(formula= decline ~ condition, data= na.omit(vocerrs))
bf2

## POSSION REGRESSION ##
# Here I use a possion regression to estimate the beta using the count data. This generates a beta weight and the approach is almost identical to our approach for reaction times.
vocerrs$slope <- NA #dummy column
blocklist <- seq(1:4)
nsubkeep<-length(subinclude)
for (i in 1:nsubkeep){ #loop through subjects
  subname<-subinclude[i] #find subject ID
  myrows<-which(vocerrs$subject==subname) #select rows for this sub
  temp<-vocshort[vocshort$subject==subname,] #make a little vector with this subject's data
  mylm <- summary(glm(Attempts~ block, family="poisson", data= temp))
  vocerrs$slope[myrows[1]]<- mylm$coefficients[2,1]
}
print("one-group t-test vs zero for slopes")
t.test(vocerrs$slope[vocerrs$condition=='blocked'])
lsr::cohensD(vocerrs$slope[vocerrs$condition=='blocked'], mu= 0)
t.test(vocerrs$slope[vocerrs$condition=='interleaved'])
lsr::cohensD(vocerrs$slope[vocerrs$condition=='interleaved'], mu= 0)

print("T test comparing slopes")
t.test(vocerrs$slope ~ vocerrs$condition)
# bayes
slope_no_na <- vocerrs %>% tidyr::drop_na(slope)
lsr::cohensD(vocerrs$slope ~ vocerrs$condition)
bf = BayesFactor::ttestBF(formula= slope ~ condition, data= slope_no_na)
bf

change_Acc <- ggplot(vocerrs, aes(x=condition, y=slope, fill=condition, shape= condition, linetype= condition)) +
  geom_violin(alpha= .1, size=1) +
  geom_hline(yintercept=0, linetype="dashed",  color = "black", size=1) + 
  geom_dotplot(binaxis='y', stackdir='center', dotsize=1,alpha= 0.8) + 
  geom_boxplot(width=0.1, position=position_dodge(0.9), size=1 , notch = T, notchwidth = 0.4, varwidth =F,
               fill= 'white', color= 'black', show.legend=FALSE, linetype= 'solid') +
  theme_bw(18) + xlab(" ") + ylab("Beta-estimates: Number of attempts") + theme(legend.position="top") +
  theme(legend.position = 'none', legend.title=element_blank(), plot.title = element_text(hjust = 0.5)) +
  ylim(-.3, .3) + ggtitle("(A)")
ggpubr::ggarrange(change_Acc, change_RT)
```
